Abstract

### 2025-10-08 output/Main_text.Rmd
Explain computation of density contours in test space

Panel (a) of Figure \@ref(fig:item-plot-out) shows
the item representation in the uncorrelated case,
while the correlated case is shown in panels (b) to (d)
under different conditions.
In all the four panels, the contours of a bivariate standard normal density
with the corresponding correlation are plot along with the items
(from outer to inner, the contours are the `r contour_breaks_out` of
the density at its mode).
Note that the stretched ellipses in panel (c) are the result of transforming
the distribution in the latent space to the test space,
according to \@ref(eq:trait-coords-spaces-transform).
In panel (b), the item coordinates are computed from
the agnostic version of the parameters.
These coordinates are the same ones as in the first case, but
their relative position with respect to the latent trait distribution is not
---This is the effect of disregarding the covariance structure.
Panel (c) shows the items with their coordinates computed using
the correlation-based version of the parameters.
To keep the horizontal axis invariant,
we have defined $`r TRANSFORM_MATRIX_TRANSP_INV`$ such that
it only rotates the vertical axis [@harman_modern_1976]:

>>>>

Panel (a) of Figure \@ref(fig:item-plot-out) shows
the item representation in the uncorrelated case,
while the correlated case is shown in panels (b) to (d)
under different conditions.
In all the four panels, the contours of a bivariate standard normal density
with the corresponding correlation are plot along with the items
(from outer to inner, the contours are the `r contour_breaks_out` of
the density at its mode).
Note that the stretched ellipses in panel (c) are the result of transforming
the distribution in the latent space to the test space,
according to Equation \@ref(eq:trait-coords-spaces-transform).
This implies that the covariance matrix of the distribution projected into
the test space is transformed inversely as in the latent space, that is,
$`r COV_MATRIX_TRANSF_TS_EQ`$.

In panel (b), the item coordinates are computed from
the agnostic version of the parameters.
These coordinates are the same ones as in the first case, but
their relative position with respect to the latent trait distribution is not
---This is the effect of disregarding the covariance structure.
Panel (c) shows the items with their coordinates computed using
the correlation-based version of the parameters.
To keep the horizontal axis invariant,
we have defined $`r TRANSFORM_MATRIX_TRANSP_INV`$ such that
it only rotates the vertical axis [@harman_modern_1976]:
